%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Main Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  
%---------------------------------------------------------
  \cventry
    {Graduate School} % Title
    {FRC Biodiversity of FEB RAS} % Organization
    {Vladivostok, Russia} % Location
    {2019 - 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Specialization - Ecology. Deep data analysis, statistics, mathematical modeling of ecological processes.}
        \item {Working with spatial and time series for ecological data analysis.}
        \item {Using the R programming language, statistical methods and mathematical modeling.}
        \item {Publication of scientific articles in the field of ecology and data analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Data education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Foundation - School 21} % Degree
    {School of Programming 21} % Institution
    {Novosibirsk, Russia} % Location
    {2023 - 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {C, bash, Python, SQL, Go, Ruby, algorithms, data structures.}
        \item {Deep dive into programming languages and development methodologies.}
        \item {Peer-to-peer learning and project activities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Degree
    {Yandex Practicum} % Institution
    {Online} % Location
    {Feb. 2023 - 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Python libraries: pandas, scipy, numpy, matplotlib, scikit-learn, plotly, sqlalchemy.}
        \item {SQL queries, data analysis, machine learning.}
        \item {Statistical analysis and data visualization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Degree
    {T1 Data Engineer School} % Institution
    {Online} % Location
    {2024 - Jun. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Data engineer school from T1 holding with a graduation project.}
        \item {ETL/ELT processes, data architecture, modern tools.}
        \item {Practical projects for processing big data in Greenplum.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Arenadata Hadoop Administrator} % Degree
    {Arenadata} % Institution
    {Online} % Location
    {Jan. 2025 - Mar. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Operation of Arenadata Hadoop. HDFS, Zookeeper, Grafana, Spark, Kafka.}
        \item {Monitoring services of the Hadoop ecosystem.}
        \item {Deploying clusters in the Hadoop ecosystem.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Specialized Training}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {C/C++ Development} % Degree
    {School 21} % Institution
    {Novosibirsk, Russia} % Location
    {2023 - 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Writing standard libraries in C, data structures, algorithms.}
        \item {Memory management, writing desktop programs in C++ \& QT.}
        \item {Projects: 3dViewer, Calculator, Tetris and others.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Development} % Degree
    {School 21} % Institution
    {Novosibirsk, Russia} % Location
    {2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Dockerfile, Makefile, Ansible, Neo4j, Python.}
        \item {unittest, pytest, subprocess, bs4, dotenv, scipy, plotly.}
        \item {grpc, sqlalchemy, asyncio, fastapi, aiogram.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SQL \& Database} % Degree
    {School 21} % Institution
    {Novosibirsk, Russia} % Location
    {2024.1 - 2024.2} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {pl/pgsql, functions, procedures, window functions.}
        \item {Subqueries, CTE, nested queries, recursive queries.}
        \item {Database performance optimization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps \& Infrastructure} % Degree
    {School 21} % Institution
    {Novosibirsk, Russia} % Location
    {2024.3 - 2024.4} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Linux, VM, Docker, CI/CD, bash.}
        \item {Prometheus, Grafana, Makefile, Docker, Vagrantfile.}
        \item {Containerization and orchestration of applications, CI/CD setup.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}


\newpage

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Key Projects \& Achievements}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Science Club Leader} % Job title
    {School 21} % Organization
    {Novosibirsk, Russia} % Location
    {Mar. 2023 - Sep. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formed a community within School 21 of 60+ people.}
        \item {Conducted educational sessions in a peer-to-peer style.}
        \item {Joint participation in hackathons, developing team soft skills.}
        \item {Team leadership at hackathons and coordination of project activities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hackathon Winner} % Job title
    {SmartSocialHack} % Organization
    {Moscow, Russia} % Location
    {June. 2024 - Jul. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {First place in a case dedicated to socially significant problems.}
        \item {Using LLM, PostgreSQL, FastAPI to create a solution.}
        \item {Developing a mobile and web application as a team.}
        \item {Integration of PWA technologies to create a comprehensive solution.}
        \item {Development based on microservice architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}