%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Axenix} % Organization
    {Saint Petersburg, Russia} % Location
    {Aug. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a modular system for dynamic generation of YAML configurations for DAGs based on Excel mappings, which reduced the time for setting up new ETL processes by 40\%.}
        \item {Created a comprehensive set of development automation tools: Airflow log parser (PowerShell), synthetic data generator, artifact copying tools, and a command shell for managing Git processes, which accelerated the onboarding process for new employees and improved work quality.}
        \item {Optimized the ETL flow generator together with colleagues from other teams: implemented templating, asynchronous processing and expanded the coverage of generated artifacts.}
        \item {Automated the data quality testing process and created PL/pgSQL functions for согласующие DataFix tests, significantly reducing preparation time.}
        \item {Created and maintained stored procedures, functions, data marts and views in Greenplum for operational data quality processes.}
        \item {Provided integration of various data sources (ClickHouse, Oracle, Hive) and maintained the Data Vault 2.0 architecture.}
        \item {Organized a developer community on Telegram and GitLab to share tools and best practices.}
        \item {Developed ETL flows, prepared releases, hotfixes and data fixes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Spacecode} % Organization
    {Krasnodar, Russia (Remote)} % Location
    {Apr. 2024 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a multimodal assistant based on LLM using HuggingFace models, RAG approach, LangChain and Unstructured via LLAMA\_CPP/VLLM.}
        \item {Created a dynamic pricing system using interpretable regression models, which is estimated to increase segment profit by 15\%.}
        \item {Used Apache Airflow to develop an ETL pipeline ensuring data freshness for ML models.}
        \item {Implemented DVC for model data versioning, which greatly simplified their tracking and result reproduction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {ASK «DirectService»} % Organization
    {Novosibirsk, Russia (Remote)} % Location
    {Sep. 2023 - Jan. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented an enterprise-level Data Warehouse (DWH) from scratch on a scale of tens of terabytes of data, using PostgreSQL as the main storage and ClickHouse as the analytical storage.}
        \item {Automated the data mart update process by creating a comprehensive pipeline based on Shell scripts and Windows Task Scheduler.}
        \item {Set up a data migration mechanism from ClickHouse to PostgreSQL, ensuring uninterrupted operation of analytical systems.}
        \item {Together with system analysts, developed methodologies for monitoring and optimizing DWH performance.}
        \item {Set up monitoring based on Postgres extensions, CI/CD for verified code delivery using Flyway and Github Actions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ML Engineer} % Job title
    {LLC «ColorDent»} % Organization
    {Moscow, Russia (Remote)} % Location
    {Jun. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an ML image classifier for tooth disease diagnosis using OpenCV and TensorFlow Lite. The model achieved accuracy of over 95\% on test data.}
        \item {Integrated ML models into a mobile application using MLflow for model version management and DVC for data versioning.}
        \item {Optimized model performance for operation on resource-constrained devices, which allowed it to be used on mobile platforms without significant quality loss.}
        \item {Developed a system for tracking model training metrics and implemented automated testing to ensure high solution quality.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}